---
title: "load_42_pt"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The objective of this document is to show how we made the .rdata files of the Input-Output tables with 42 sectors.

##Table of contents
0. [Introduction](#intro)
 [Loading the data](#load)
 
### 0. Introduction {#intro}

We consider that the user working directory at this point is the gicRio folder.

```{r , echo=FALSE}
#Loading libraries
library(magrittr)
library(readxl)
#setting objects as the folders reference
folder_gicRio <- "~/gicRio"
folder_data <-  "~/gicRio/data"
folder_rawdata <- "~/gicRio/data/raw_data"
folder_finaldata <- "~/gicRio/data/final_data"
folder_intermediarydata <- "~/gicRio/data/intermediary_data"

#Creating a funct

```

## Loading the data{#load}

### 1. Reading the labels

In this part we are going to read the collumn names and row names, in portuguese, and transform they into objects.
```{r, echo = false}
setwd(folder_rawdata)
label_GIC_42_pt <- read_excel("MIP_42/MIP_2000_42.xlsx", sheet = "D", range = "A6:A47", col_names = FALSE)

label_GIC_91_pt <- read_excel("MIP_42/MIP_2000_42.xlsx", sheet = "Usos Nacional", range = "A6:A96", col_names = FALSE)

label_finaldemand_pt <- read_excel("MIP_42/MIP_2000_42.xlsx", sheet = "Usos Nacional", range = "AT4:AY4", col_names = FALSE)

label_demand_pt <- read_excel("MIP_42/MIP_2000_42.xlsx", sheet = "Usos Nacional", range = "AS4:AY4", col_names = FALSE)

label_demand_pt[1] <- "Consumo Intermediário Total"

label_col_nationaluse_pt <- read_excel("MIP_42/MIP_2000_42.xlsx", sheet = "Usos Nacional", range = "C4:BA4", col_names = FALSE)

sector_description_91_pt <- read_excel("MIP_42/MIP_2000_42.xlsx", sheet = "Usos Nacional", range = "B6:B96", col_names = FALSE)

sector_description_42_pt <- read_excel("MIP_42/MIP_2000_42.xlsx", sheet = "Usos Nacional", range = "C4:AR4", col_names = FALSE)

```

